Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2024-04-07 demystify.tex
updates

\emph{Research faculty} or research scientists are typically non-tenure line faculty who focus on research. While they cannot serve as a formal adviser, they often co-advise and mentor students with tenure-line faculty. They can recruit students and provide RA funding for them as they typically have their own funding.

>>>>

\emph{Research faculty} or research scientists are typically non-tenure line faculty who focus on research (e.g., publishing papers and getting grants). While they cannot serve as a formal adviser, they often co-advise and mentor students with tenure-line faculty. They can recruit students and provide RA funding for them.
